%%%%%%%%%%%%%%%%%%%%%%%%%%
%!TEX program = xelatex
% farhan - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/farhandas/farhan-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{farhan-resume-openfont}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{}{Farhan \textbf{Sadeek}}{\urlstyle{same}\href{https://farhan-sadeek.vercel.app/}{farhan-sadeek.vercel.app | }
    \href{mailto:farhansadeek019@gmail.com}{farhansadeek019@gmail.com} | 614-384-1832}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.25\textwidth}

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     EDUCATION
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \section{Education}

    \subsection{\href{https://www.dublinschools.net/Coffman}{Dublin Coffman HS}}
    \descript{High School Diploma}
    \descript{May 2025 | Dublin, OH}
    \texttt{Cum. GPA: 4.56 / 4.0} \\
    AP Physics C: Mechanics \\
    AP Physics C: Electricity \& Magnetism \\
    AP Calculus BC \\
    AP Computer Science A\\
    AP Chemistry\\
    AP Macro/Microeconomics*\\
    \sectionsep
    \subsection{\href{https://www.osu.edu/}{The Ohio State University}}
    \descript{Dual Enrollment in High School}
    \descript{Math/Stat, Physics, CS, ECE}
    \descript{Aug 2025 | Columbus, OH}
    \texttt{Cum. GPA: 3.826 / 4.0} \\
    Number Theory* \\
    Real Analysis* \\
    Abstract Algebra* \\
    Mathematical Statistics* \\
    Relativity / Quantum Mechanics* \\
    Probability Theory \\
    Classical Mechanics \\
    Mathematical Logic and Proofs \\
    Partial Differential Equations \\
    Linear Algebra\\
    Multi-variable Calculus\\
    Discrete Mathematics\\
    Data Structures \\
    Object-Oriented Programming\\
    Software Development and Design\\
    Engineering Physics\\

    \sectionsep
    \subsection{\href{https://stanford.edu/}{Stanford University}}
    \descript{Stanford, CA}
    Data Analysis with Python \\
    Data Structures and Algorithms\\
    Statistics and Machine Learning \\

    \textsubscript{* Current year courses}

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     SKILLS
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Skills}
    \subsection{Programming}
    \location{Over 5000 lines:}
    Java \textbullet{}   C++ \textbullet{} Python \textbullet{} Javascript \\
    HTML \textbullet{} CSS \textbullet \LaTeX \\
    \location{Over 1000 lines:}
    C \textbullet{} R \textbullet{} CSS \textbullet{} \textbullet{} MySQL \\
    \vspace{1em}
    \subsection{Tools \& Frameworks}
    Tableau \textbullet{} Tidyverse \textbullet{} Tensorflow \\ React \textbullet{}
    PyTorch \textbullet{} Excel \textbullet{} Pandas\\ Plotly

    \sectionsep

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     AWARDS
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Awards}
    \subsection{2024}
    \href{https://hack.osu.edu/hs/fall-2023/}{Ohio State Hackathon Winner} \\
    USA Computing Olympiad Gold \\
    Gates Scholarship Semifinalist
    \subsection{2023}
    \href{https://hack.osu.edu/hs/fall-2023/}{Ohio State Hackathon Winner} \\

    \subsection{2022}
    {AP Scholar with Distinction} \\
    {Ohio State Hackathon Winner} \\
    \subsection{2021}
    \href{https://www.aapt.org/physicsteam/2024/index.cfm}{Bangaldesh Physics Olympiad Semifinalist} \\
    \href{https://www.acs.org/education/students/highschool/olympiad.html}{Bangaldesh Chemistry Olympiad Semifinalist} \\

    \section{Activities}
    \href{https://cpcosu.github.io/}{Competitive Programming Club} \\
    \href{https://bdaaosu.org/}{Big Data and Analytics Association} \\
    \href{https://www.osuaiclub.com/}{Artificial Intelligence Club} \\
    Google Developer's Club

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %
    %     COLUMN TWO
    %
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.70\textwidth}

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     EXPERIENCE
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Experience}
    \runsubsection{\href{https://www.expedia.com/}{Expedia Group}\hspace{3pt}$|$}
    \descript{Software Engineer}
    \location{June 2024 - Present | Seattle, WA}
    $ \vrule $
    \begin{tightemize}
        \item Developed machine learning models to analyze travel data and identify growth
        opportunities, leading to an \textbf{18\%} increase in customer retention and a
        \textbf{22\%} boost in booking accuracy.
        \item Streamlined competitor benchmarking by automating data aggregation processes,
        reducing analysis time by \textbf{40\%} and improving actionable insights
        delivery by \textbf{30\%}.
        \item Collaborated with engineering and product teams to integrate market
        intelligence into platform enhancements, resulting in a \textbf{25\%}
        improvement in user experience scores and a \textbf{15\%} reduction in customer
        churn.
    \end{tightemize}
    \sectionsep
    \runsubsection{\href{https://www.spectrum.net/}{Spectrum} \hspace{3pt}$|$}
    \descript{Technical Solutions Engineer}
    \location{June 2023 - April 2024 | Columbus, OH}
    \begin{tightemize}
        \item Advised over \textbf{200} clients monthly on network solutions, including VoIP,
        MPLS, and SIP technologies, contributing to a \textbf{12\%} increase in
        long-term contract renewals and a \textbf{20\%} reduction in support tickets.
        \item Designed and presented technical proposals tailored to client needs, achieving
        a \textbf{25\%} rise in sales conversions and a \textbf{30\%} increase in
        customer engagement metrics.
        \item Trained sales teams on advanced technical features, leading to a \textbf{15\%}
        improvement in team productivity and boosting client satisfaction scores by
        \textbf{18\%}.
    \end{tightemize}
    \sectionsep

    \runsubsection{\href{https://renaissancetech.com/}{RenaissanceTech}\hspace{3pt}$|$}
    \descript{Software Engineer}
    \location{May 2024 - Aug 2024 | Dublin, OH}
    \begin{tightemize}
        \item Developed and maintained dynamic, high-performance web applications using
        React, achieving a \textbf{30\%} increase in user engagement, a \textbf{25\%}
        reduction in page load times, and a \textbf{40\%} increase in feature adoption
        within 6 months.
        \item Implemented 15 reusable components and optimized front-end architecture,
        reducing development time by \textbf{20\%} and boosting user satisfaction
        scores by \textbf{15\%} through improved UI/UX.
    \end{tightemize}
    \sectionsep

    \runsubsection{\href{https://www.osu.edu/}{The Ohio State University}\hspace{3pt}$|$}
    \descript{Lead Machine Learning Engineer}
    \location{Mar 2024 – Present | Columbus, OH}
    \begin{tightemize}
        \item Developed and maintained data pipelines to facilitate efficient ETL of
        large-scale datasets, ensuring high data quality and integrity.
        \item Collaborated with cross-functional teams to optimize database schemas and
        algorithms for effective storage and retrieval of time-sensitive data, and
        managed automated processes for data validation and cleansing.
    \end{tightemize}
    \sectionsep

    \runsubsection{\href{https://www.netsteady.com/}{NetSteady}\hspace{3pt}$|$}
    \descript{Automation Programmer}
    \location{May 2024 - Aug 2024 | Hilliard, OH}
    \begin{tightemize}
        \item Designed and implemented automated testing frameworks and scripts, achieving a
        \textbf{35\%} reduction in manual testing efforts and a \textbf{20\%} increase
        in bug detection rates, alongside a \textbf{30\%} decrease in system outages
        due to proactive monitoring.
        \item Created custom automation solutions for data processing and system integration,
        increasing operational efficiency by \textbf{40\%}, reducing system downtime by
        \textbf{15\%}, and leading to a \textbf{20\%} improvement in team productivity
        through comprehensive documentation and training.
    \end{tightemize}
    \section{Projects}
    \subsection{{CrisisCompass}}
    \begin{tightemize}     \vspace{10pt}
        \item Developed a disaster assessment tool using YOLO object detection models to
        analyze satellite imagery, achieving \textbf{92\%} accuracy in identifying
        flood damage and compromised structures.
        \item Optimized cloud deployment workflows on AWS, reducing model training time by
        \textbf{40\%} and enabling real-time predictions.
        \item Designed an intuitive dashboard to visualize disaster impact data, providing
        first responders with actionable insights for time-critical decisions.
    \end{tightemize}
    \sectionsep

    \subsection{\href{https://arduino.cc/}{VisionScope}}
    \begin{tightemize}
        \vspace{10pt}
        \item Developed a real-time video processing system using an Arduino microcontroller
        and infrared sensors, enabling face detection through optimized cascade
        classifiers.
        \item Achieved efficient machine learning inference by optimizing computational
        workflows, balancing algorithmic complexity with the limitations of embedded
        systems.
        \item Enhanced understanding of embedded AI by exploring the intersection of systems
        programming and statistical learning.
    \end{tightemize}
    \sectionsep

    \subsection{{UniMind}}
    \begin{tightemize}
        \vspace{10pt}
        \item Designed and developed a React-based application with ChainLit integration,
        centralizing access to multiple leading LLMs in one platform.
        \item Built an intuitive and responsive interface for diverse applications, including
        content generation, code assistance, and data analysis.
        \item Engineered a robust backend to manage API connections, ensuring
        optimized performance and scalability across models.
    \end{tightemize}
    \section{Research}
    \begin{tightemize}
        \vspace{10pt}
        \item Investigated the impact of natural disasters on individuals with diverse identities under the guidance of Dr. Kelsea Best, analyzing patterns in disaster response and resilience.
        \item Utilized Python (Pandas, Matplotlib) and R (Tidyverse, ggplot2) for data preprocessing, visualization, and statistical analysis, delivering comprehensive insights and reports to aid ongoing research.
    \end{tightemize}
\end{minipage}
\end{document}
\documentclass[]{article}
