%%%%%%%%%%%%%%%%%%%%%%%%%%
%!TEX program = xelatex
% farhan - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/farhandas/farhan-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{Farhan_Resume_Class}
\usepackage{fancyhdr}
\usepackage{fontspec}
\pagestyle{fancy}
\fancyhf{}
\usepackage{xcolor}
\definecolor{linkblue}{HTML}{0450C2}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{}{Farhan \textbf{Sadeek}}{\urlstyle{same}\href{https://farhansadeek.com}{\textcolor{linkblue}{farhansadeek.com}}  | \href{https://academic.farhansadeek.com}{\textcolor{linkblue}{academic.farhansadeek.com}} | 
    \href{mailto:sadeekfarhan21@gmail.com}{\textcolor{linkblue}{sadeekfarhan21@gmail.com}} | 617-939-9262}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.25\textwidth}

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     EDUCATION
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \section{Education}
    \subsection{\href{https://dartmouth.edu/}{Dartmouth College}}
    \descript{AB in Math, CS, Economics}
    \descript{June 2029 | Hanover, NH}
    \texttt{Cum. GPA: 4.0 / 4.0} \\
    
    \sectionsep
    \subsection{\href{https://www.osu.edu/}{The Ohio State University}}
    \descript{Dual Enrollment in High School}
    \descript{Math/Stat, Physics, CS, ECE}
    \descript{Aug 2025 | Columbus, OH}
    \texttt{Cum. GPA: 3.7 / 4.0} \\
    Number Theory / Abstract Algebra \\
    Real Analysis \\
    Mathematical Statistics \\
    Relativity / Quantum Mechanics \\
    Probability Theory \\
    Classical Mechanics \\
    Mathematical Logic and Proofs \\
    Partial Differential Equations \\
    Linear Algebra\\
    Multi-variable Calculus\\
    Discrete Mathematics\\
    Data Structures \\
    Object-Oriented Programming\\
    Software Development and Design\\

    \sectionsep
    \subsection{\href{https://www.dublinschools.net/Coffman}{Dublin Coffman HS}}
    \descript{High School Diploma}
    \descript{May 2025 | Dublin, OH}
    \texttt{Cum. GPA: 4.55 / 4.0} \\
    AP Physics C \\
    AP Calculus BC \\
    AP Computer Science A\\
    AP Chemistry\\
    AP Macro/Microeconomics*\\


    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     LINKS
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
\sectionsep    
\section{Links}
Github: \href{https://github.com/SadeekFarhan21}{\bf SadeekFarhan21} \\
LinkedIn:  \href{https://www.linkedin.com/in/farhansadeekde110/}{\bf farhansadeekde110} \\

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     SKILLS
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Skills}
    \subsection{Programming}
    \location{Over 5000 lines:}
    Java \textbullet{}   C++ \textbullet{} Python \textbullet{} Javascript \\
    HTML \textbullet{} CSS \textbullet \LaTeX \\
    \location{Over 1000 lines:}
    C \textbullet{} R \textbullet{} CSS \textbullet{} \textbullet{} MySQL \\
    \vspace{1em}
    \subsection{Tools \& Frameworks}
    Tableau \textbullet{} Tidyverse \textbullet{} Tensorflow \\ React \textbullet{}
    PyTorch \textbullet{} Excel \textbullet{} Pandas\\ Plotly

    \sectionsep

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     AWARDS
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Awards}
    \subsection{2024}
    \href{https://hack.osu.edu/hs/fall-2023/}{Ohio State Hackathon Winner} \\
    USA Computing Olympiad Gold \\
    Gates Scholarship Semifinalist
    \subsection{2023}
    \href{https://hack.osu.edu/hs/fall-2023/}{Ohio State Hackathon Winner} \\

    \subsection{2022}
    {AP Scholar with Distinction} \\
    {Ohio State Hackathon Winner} \\
    \subsection{2021}
    \href{https://www.aapt.org/physicsteam/2024/index.cfm}{Physics Olympiad Semifinalist} \\
    \href{https://www.acs.org/education/students/highschool/olympiad.html}{Chemistry Olympiad Semifinalist} \\

    \section{Activities}
    \href{https://cpcosu.github.io/}{Competitive Programming Club} \\
    \href{https://bdaaosu.org/}{Big Data and Analytics Association} \\
    \href{https://www.osuaiclub.com/}{Artificial Intelligence Club} \\
    Google Developer's Club

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %
    %     COLUMN TWO
    %
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.70\textwidth}

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     EXPERIENCE
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Experience}
    \runsubsection{\href{https://www.osu.edu/}{The Ohio State University}\hspace{3pt}$|$}
    \descript{Student Assistant Instructor}
    \location{Jan 2025 – Present | Columbus, OH}
    $ \vrule $
    \begin{tightemize}
        \item Assisted in teaching CSE 2231: Software Development and Design, providing
        guidance on object-oriented programming principles, design patterns, and
        software engineering best practices.
        \item Conducted lab sessions and office hours to support students in understanding
        course material, debugging code, and completing assignments.
    \end{tightemize}
    \sectionsep
    \runsubsection{\href{https://www.expedia.com/}{Expedia Group}\hspace{3pt}$|$}
    \descript{Software Engineer}
    \location{June 2024 - Aug 2024 | Seattle, WA}
    \begin{tightemize}
        \item Developed machine learning models to analyze travel data and identify growth
        opportunities, leading to an \textbf{18\%} increase in customer retention and a
        \textbf{22\%} boost in booking accuracy.
        \item Streamlined competitor benchmarking by automating data aggregation processes,
        reducing analysis time by \textbf{40\%} and improving actionable insights
        delivery by \textbf{30\%}.
        \item Collaborated with engineering and product teams to integrate market
        intelligence into platform enhancements, resulting in a \textbf{25\%}
        improvement in user experience scores and a \textbf{15\%} reduction in customer
        churn.
    \end{tightemize}
    \sectionsep
    \runsubsection{\href{https://www.spectrum.net/}{Spectrum} \hspace{3pt}$|$}
    \descript{Technical Solutions Engineer}
    \location{June 2023 - April 2024 | Columbus, OH}
        \begin{tightemize}
            \item Advised over \textbf{200} clients monthly on network solutions, including VoIP,
            MPLS, and SIP technologies, contributing to a \textbf{12\%} increase in
            long-term contract renewals and a \textbf{20\%} reduction in support tickets.
            \item Designed and presented technical proposals tailored to client needs, achieving
            a \textbf{25\%} rise in sales conversions and a \textbf{30\%} increase in
            customer engagement metrics.
            \item Collaborated with sales teams to provide technical insights, leading to a \textbf{15\%}
            improvement in team productivity and boosting client satisfaction scores by
            \textbf{18\%}.
    \end{tightemize}
    \sectionsep

    \runsubsection{\href{https://renaissancetech.com/}{RenaissanceTech}\hspace{3pt}$|$}
    \descript{Software Engineer}
    \location{May 2024 - Aug 2024 | Dublin, OH}
    \begin{tightemize}
        \item Developed and maintained dynamic, high-performance web applications using
        React, achieving a \textbf{30\%} increase in user engagement, a \textbf{25\%}
        reduction in page load times, and a \textbf{40\%} increase in feature adoption
        within 6 months.
        \item Implemented 10 reusable components and optimized front-end architecture,
        reducing development time by \textbf{20\%} and boosting user satisfaction
        scores by \textbf{15\%} through improved UI/UX.
    \end{tightemize}
    \sectionsep

    \runsubsection{\href{https://www.netsteady.com/}{NetSteady}\hspace{3pt}$|$}
    \descript{Automation Programmer}
    \location{May 2024 - Aug 2024 | Hilliard, OH}
    \begin{tightemize}
        \item Designed and implemented automated testing frameworks and scripts, achieving a
        \textbf{35\%} reduction in manual testing efforts and a \textbf{20\%} increase
        in bug detection rates, alongside a \textbf{30\%} decrease in system outages
        due to proactive monitoring.
        \item Created custom automation solutions for data processing and system integration,
        increasing operational efficiency by \textbf{40\%}, reducing system downtime by
        \textbf{15\%}, and leading to a \textbf{20\%} improvement in team productivity
        through comprehensive documentation and training.
    \end{tightemize}
    \section{Projects}
\subsection{\href{https://notes.farhansadeek.com}{College Notes} \hfill \href{https://notes.farhansadeek.com}{\lowercase{notes.farhansadeek.com}}}
        \begin{tightemize}
            \vspace{10pt}
            \item Created detailed LaTeX notes for Physics, Math, and CS classes, including equations, diagrams, and code snippets for clarity.
            \item Organized notes by semester and subject for easy reference, continuously updating them based on lectures.
            \item Hosted notes on my website for peer access, facilitating collaborative learning and resource sharing.
        \end{tightemize}
    \subsection{\href{https://photos.farhansadeek.com}{Personal Photography} \hfill \href{https://photos.farhansadeek.com}{\lowercase{photos.farhansadeek.com}}}
    \begin{tightemize}
        \vspace{10pt}
        \item Used a pre-built \texttt{react} template to efficiently create a dynamic portfolio website showcasing photography projects. 
\item Integrated a user-friendly interface with smooth animations and a responsive design to attract and engage visitors effectively. 
\item Used an image optimization library to reduce loadtime while keeping the visual quality intact, resulting in an improved user experience. 
    \end{tightemize}

    \subsection{\href{https://github.com/SadeekFarhan21/QuantifyAI/}{QuantifyAI}\hfill \href{https://github.com/SadeekFarhan21/Quantathon/}{\lowercase{github.com/SadeekFarhan21/QuantifyAI}}}
    \begin{tightemize}     \vspace{10pt}
    \item Conducted a comprehensive analysis of financial data from 2007 to 2022, using data from 2007 to 2018 for training a predictive model and data from 2019 to 2022 for testing.
    \item Developed and implemented a machine learning model to forecast stock prices, achieving a Sharpe ratio of 1.1, which indicates a significantly higher return per unit of risk compared to the S\&P 500 benchmark.
    \item Utilized Python libraries such as Pandas, NumPy, Scikit-learn, TensorFlow, Matplotlib, and Seaborn for data preprocessing, feature engineering, model training, evaluation, and generating detailed performance reports and visualizations.
    \end{tightemize}

    \subsection{\href{https://github.com/SadeekFarhan21/SignifyAI}{SignifyAI} \hfill \href{https://github.com/SadeekFarhan21/SignifyAI/}{\lowercase{github.com/SadeekFarhan21/SignifyAI}}}
    \begin{tightemize}
        \vspace{10pt}
        \item Developed a real-time emotion detection system that parses the entire screen of a laptop and runs a machine learning model locally to predict emotions.
        \item Implemented an assistive speech detection feature for individuals with speaking disabilities, enhancing accessibility and communication.
        \item Achieved efficient machine learning inference by optimizing computational workflows, balancing algorithmic complexity with the limitations of embedded systems.
    \end{tightemize}

    \section{Research}
    \begin{tightemize}
        \vspace{10pt}
        \item Investigated the impact of natural disasters on individuals with diverse
        identities under the guidance of Dr. Kelsea Best, analyzing patterns in
        disaster response and resilience.
        \item Utilized Python (Pandas, Matplotlib) and R (Tidyverse, ggplot2) for data
        preprocessing, visualization, and statistical analysis, delivering
        comprehensive insights and reports to aid ongoing research.
    \end{tightemize}
\end{minipage}
\end{document}
\documentclass[]{article}